Species motif participation provides unique information about species risk of extinction

### 2022-06-16 manuscript/supplement_motifs.tex
Updates from Overleaf

        Although previous work has shown that the niche model replicates the motif structure of empirical networks~\citep{Stouffer2005a,Stouffer2006}, we additionally provide a comparison of the motif profiles and consumer motif participation for our simulated networks and the highest-quality empirical networks we could find within the same size range.
        For this comparison, we obtained all networks containing 50-100 species from \citet{globalwebdb}.
        These webs ranged in connectance from 0.024-0.089.
        We then removed networks where sets of predators and prey were completely different (i.e., bipartite networks) or links were not clear (i.e., +/- effects rather than predation specifically).
        This yielded five vertebrate-dominated food webs describing the California coast in different years, four invertebrate-dominated food webs describing mainland US streams, 23 invertebrate-dominated food webs describing New Zealand streams, and five other invertebrate-dominated food webs.
        This final set of webs had 50-77 species and connectances of 0.2-0.21 - the upper range of connectance in our simulations.
        This may be partly due to relatively poor resolution of basal resources in these empirical webs: aggregation of many taxa into nodes such as `phytoplankton' will tend to decrease the number of species but leave the number of links unchanged, raising connectance.
        We note that most of these webs were compiled by just three research groups.
        Moreover, many of the webs are repeated samples of the same site  or closely-grouped sites.
        This means that these empirical networks cannot be considered fully independent samples.

>>>>

        Although previous work has shown that the niche model replicates the motif structure of empirical networks~\citep{Stouffer2005a,Stouffer2006}, we additionally provide a comparison of the motif profiles and consumer motif participation for our simulated networks and the highest-quality empirical networks we could find within the same size range.
        For this comparison, we obtained all networks containing 50-100 species from \citet{globalwebdb}.
        We then removed networks where sets of predators and prey were completely different (i.e., bipartite networks) or links were not clear (i.e., +/- effects rather than predation specifically).
        This yielded five vertebrate-dominated food webs describing the California coast in different years, four invertebrate-dominated food webs describing mainland US streams, 23 invertebrate-dominated food webs describing New Zealand streams, and five other invertebrate-dominated food webs.
        This final set of webs had 50-77 species and connectances (after rendering the networks acyclic) of 0.095-0.227 - covering the upper half of the connectance range we simulate, as well as slightly higher connectances.
        This may be partly due to relatively poor resolution of basal resources in these empirical webs: aggregation of many taxa into nodes such as `phytoplankton' will tend to decrease the number of species but leave the number of links unchanged, raising connectance.
        We note that most of these webs were compiled by just three research groups.
        Moreover, many of the webs are repeated samples of the same site  or closely-grouped sites.
        This means that these empirical networks cannot be considered fully independent samples.
